Parameter estimation

### 2023-10-10 SFE_article_Parameter_Estimation/Article_Model_Parameters.tex
10.10

This study presented basic aspects regarding the laboratory work for obtaining caraway extracts using supercritical carbon dioxide at different operating conditions. A first-principle process model was developed based on governing equations. Based on the literature review, the extraction kinetic model was selected and combined with the general mass balance equations. The values of unknown parameters in the process model were obtained by parameter estimation. The yield data from the experiments were compared against the yield data generated by the model. The IPOPT solver was used to solve the maximum likelihood estimation. The process model was found to have good agreement with experimental yield curves. Later, the parameters found for each experiment were combined to obtain more general relationships. The correlations for diffusion and decay coefficients are presented as a function of fluid density or Reynolds number. It should be noted that obtained correlations have been prepared with a limited amount of data. These correlations can be used to study qualitatively the impact of different operating conditions on the extraction yield by different methods, such as sensitivity analysis. Moreover, the generalized model could be useful in finding the optimal operating conditions with respect to the process economy.

@@

\iffalse
\newpage
\begin{table*}[p]
		\caption{Notation}
		\label{tab::symbols}
		\begin{tabular}{ |c|l|c| } 
			\hline
			Symbol 		& 	Description 							& Unit 						\\ \hline
			$A$			&	cross-section							& $m^2$ 					\\ \hline
			$c$			&	concentration in fluid phase			& $kg ~ m^{-3}$				\\ \hline
			$Cp$		&	specific heat of the fluid				& $J ~ mol^{-1} ~ K^{-1}$ 	\\ \hline
			$Cp_s$		&	specific heat of the solid				& $J ~ mol^{-1} ~ K^{-1}$ 	\\ \hline
			$D_e^M$		&	axial mass diffusion coefficient		& $m^2 ~ s^{-1}$			\\ \hline
			$D_e^T$		&	axial heat diffusion coefficient		& $m^2 ~ s^{-1}$			\\ \hline
			$Di$		&	internal diffusion coefficient			& $m^2 ~ s^{-1}$			\\ \hline
			$dp$		&	particle diameter						& $m$						\\ \hline
			$F(t)$		&	mass flow-rate							& $kg ~ s^{-1}$				\\ \hline
			$km$		&	partition coefficient					& $[-]$						\\ \hline
			$k^T$		&	thermal conductivity					& $W ~ m^{-1} ~ K^{-1}$		\\ \hline
			$l$			&	characteristic dimension				& $m$						\\ \hline
			$L$			&	total length of the bed					& $m$						\\ \hline
			$m$			&	mass of the oil in solid phase			& $kg$						\\ \hline
			$m_0$		&	initial mass of the oil in solid phase	& $kg$						\\ \hline
			$M_{CO_2}$	&	molecular mass of CO2					& $mol ~ kg^{-1}$			\\ \hline
			$Np$		&	number of model parameters and control variables & $[-]$			\\ \hline
			$N_{\theta}$&	number of model parameters				& $[-]$						\\ \hline
			$Nu$		&	number of control variables				& $[-]$						\\ \hline
			$Nz$		&	number of grid points in z-direction	& $[-]$						\\ \hline
			$p$			&	vector of model parameters and control variables	& $[-]$			\\ \hline
			$P(t)$		&	pressure								& $bar$						\\ \hline
			$Pe$		&	Peclet's number							& $[-]$						\\ \hline
			$q$			&	concentration in solid phase			& $kg ~ m^{-3}$				\\ \hline
			$R$			&	gas constant							& $J ~ K^{-1} ~ mol^{-1}$	\\ \hline
			$Re$		&	Reynolds number							& $[-]$						\\ \hline
			$t$			&	time									& $s$						\\ \hline
			$T$			&	temperature								& $K$						\\ \hline
			$T_0$		&	initial temperature						& $K$						\\ \hline
			$V$			&	volume of the extractor					& $m^3$						\\ \hline
			$y$			&	yield	 								& $[-]$						\\ \hline
			$z$			&	length									& $m$						\\ \hline
			$Z$			&	compressibility	factor					& $[-]$						\\ \hline
			$\epsilon$	&	void fraction							& $[-]$						\\ \hline
			$\rho$		&	density of the fluid					& $kg ~ m^{-3}$				\\ \hline
			$\rho_s$	&	solid density							& $kg ~ m^{-3}$				\\ \hline
			$\mu$		&	shape coefficient						& $[-]$						\\ \hline
			$\theta$	&	vector of model parameters				& $[-]$						\\ \hline
			$\eta$		&	viscosity								& $cP$						\\ \hline				
						& 											&							\\ \hline			
		 	Subscript	& 											&							\\ \hline
			$0$			&	initial conditions						& $[-]$						\\ \hline
			$^*$		&	equilibrium conditions					& $[-]$						\\ \hline							
		\end{tabular}
\end{table*}
\fi
\end{document}

>>>>

This study presented basic aspects regarding the laboratory work for obtaining caraway extracts using supercritical carbon dioxide at different operating conditions. A first-principle process model was developed based on governing equations. As a result of the literature review, the extraction kinetic model was selected and combined with the general mass balance equations. The values of unknown parameters in the process model were obtained by parameter estimation. The yield data from the experiments were compared against the yield generated by the model. The IPOPT solver was used to solve the maximum likelihood estimation. The process model was found to have good agreement with experimental yield curves. Later, the parameters found for each experiment were combined to obtain more general relationships. The correlations for diffusion and decay coefficients are presented as a function of fluid density or Reynolds number. It should be noted that obtained correlations have been prepared with a limited amount of data. These correlations can be used to study qualitatively the impact of different operating conditions on the extraction yield by different methods, such as sensitivity analysis. Moreover, the generalized model could be useful in finding the optimal operating conditions with respect to the process economy.

@@

\end{document}

### 2023-10-10 SFE_article_Parameter_Estimation/Sections/Results.tex
10.10

    \begin{figure*}[!h]
    	\centering
    	\begin{subfigure}[b]{\columnwidth}
    		\centering
    		\includegraphics[trim = 2cm 10.5cm 2.5cm 2.02cm,clip,width=\textwidth]{/Results_estimation/Fitting_LUKE_T40_P200.pdf}
    		\caption{Experiment at $40~^\circ C$ and 200 bar}
    	\end{subfigure}
    	\begin{subfigure}[b]{\columnwidth}
    		\centering
    		\includegraphics[trim = 2cm 10.5cm 2.5cm 2.02cm,clip,width=\textwidth]{/Results_estimation/Fitting_LUKE_T50_P200.pdf}
    		\caption{Experiment at $50~^\circ C$ and 200 bar}
    	\end{subfigure}
    	\hfill
    	\begin{subfigure}[b]{\columnwidth}
    		\centering
    		\includegraphics[trim = 2cm 10.5cm 2.5cm 2.02cm,clip,width=\textwidth]{/Results_estimation/Fitting_LUKE_T40_P300_org.pdf}
    		\caption{Experiment at $40~^\circ C$ and 300 bar}
    	\end{subfigure}
    	\begin{subfigure}[b]{\columnwidth}
    		\centering
    		\includegraphics[trim = 2cm 10.5cm 2.5cm 2.02cm,clip,width=\textwidth]{/Results_estimation/Fitting_LUKE_T50_P300_org.pdf}
    		\caption{Experiment at $50~^\circ C$ and 300 bar}
    	\end{subfigure}
    	\caption{Results of parameter estimation}
    	\label{fig: estimation_results}
    \end{figure*}

@@

	The Figure \ref{fig:Di_upsilon_res} shows how the internal diffusivity ${\color{black}D_i}$ (Equation \ref{EQ: C_sat_function}) as a function of the solute concentration in the solid phase at different operating conditions. The higher the density, the higher solubility according to \citet{Shojaie2010}, which results in higher values of the internal diffusion coefficient and larger curvature of ${\color{black}D_i}$ function.

@@

	The axial diffusion coefficient obtained from the optimizer is relatively high compared to the internal diffusion coefficients. The values of ${\color{black}D_e^M}$ have a similar order of magnitude as reported in the literature (\citet{ReisVasco2000}). %The relatively high values of the axial diffusion coefficients might be justified by taking into account the low values of the flow rate used in all the experiments. 
	The axial diffusion can be further analyzed by defining the Peclet number $\left( {\color{black}Pe} = \frac{v d_p}{D_e^M} \right)$ and the Reynolds number $\left( {\color{black}Re} = \frac{v d_p}{\mu} \right)$, where ${\color{black}d_p}=0.15~[m]$ is the characteristic dimension defined to be the extractor diameter and $\mu$ is the fluid viscosity. %The obtained Pecelt numbers have the order of magnitude of $1 \times 10^{8}$, which suggests that diffusion is negligible and advection dominates mass transport. 
	The obtained Pecelt numbers are ${\color{black}Pe} \gg 1$, which suggests that mass diffusion is negligible and advection dominates mass transport. This observation suggests that the process model could be further simplified by neglecting the diffusion term. Nevertheless, such a simplification has not been introduced in this work.
	\citet{Chung1968} presented an idea for a relationship between the Peclet (indirectly the mass diffusion coefficient) and Reynolds numbers. By modifying the idea of \citet{Chung1968}, a direct relation between the diffusion coefficient and the Reynolds number is used in the work as shown in Figure \ref{fig: results_De}. The obtained values of the mass diffusion coefficient increase almost linearly with the increment of the Reynolds number, which is in agreement with the observation that the advection dominates the diffusion.

@@

	The initial state estimation resulted in values of $\tau$ in the range from 0.69 to 0.76. These values are relatively similar to each other. In the equipment used in this experiment, around 30\% of the solute was extracted to the fluid phase during the preparation period.

	The noise present in each dataset is quantified by the parameter $\sigma^2$. It can be observed dataset obtained at $40~^\circ C$ / 200 bar and $30~^\circ C$ / 300 bar have similar value of $\sigma^2\approx0.07$. The slightly better results were obtained for the experiment at $50~^\circ C$ / 300 bar when $\sigma^2\approx0.05$. The noisiest dataset corresponds to $50~^\circ C$ / 200 bar when $\sigma^2\approx0.12$. All values of $\sigma^2$ are relatively low, suggesting the mathematical model can mimic the physical system up to the noise coming from the experiment.

>>>>

@@

	The Figure \ref{fig:Di_upsilon_res} shows how the internal diffusivity ${\color{black}D_i}$ (Equation \ref{EQ: C_sat_function}) as a function of the solute concentration in the solid phase at different operating conditions. The higher the density, the higher solubility according to \citet{Shojaie2010}, which results in higher values of the internal diffusion coefficient and steeper curvature of ${\color{black}D_i}$ function.

@@

	The axial diffusion coefficient obtained from the optimizer is relatively high compared to the internal diffusion coefficients. The values of ${\color{black}D_e^M}$ have a similar order of magnitude as reported in the literature (\citet{ReisVasco2000}). %The relatively high values of the axial diffusion coefficients might be justified by taking into account the low values of the flow rate used in all the experiments. 
	The axial diffusion can be further analyzed by defining the Peclet number $\left( {\color{black}Pe} = \frac{v d_p}{D_e^M} \right)$ and the Reynolds number $\left( {\color{black}Re} = \frac{v d_p}{\mu} \right)$, where ${\color{black}d_p}=0.15~[m]$ is the characteristic dimension defined to be the extractor diameter and $\mu$ is the fluid viscosity. %The obtained Pecelt numbers have the order of magnitude of $1 \times 10^{8}$, which suggests that diffusion is negligible and advection dominates mass transport. 
	The obtained Pecelt numbers are ${\color{black}Pe} \gg 1$, which suggests that mass diffusion is negligible and advection dominates mass transport. This observation suggests that the process model could be further simplified by neglecting the diffusion term. 
	\citet{Chung1968} presented an idea for a relationship between the Peclet (indirectly the mass diffusion coefficient) and Reynolds numbers. By modifying the idea of \citet{Chung1968}, a direct relation between the diffusion coefficient and the Reynolds number is used in the work as shown in Figure \ref{fig: results_De}. The obtained values of the mass diffusion coefficient increase almost linearly with the increment of the Reynolds number, which is in agreement with the observation that the advection dominates the diffusion.

@@

	The initial state estimation resulted in values of $\tau$ in the range from 0.69 to 0.76. In the equipment used in this experiment, around 25\%-30\% of the solute was extracted to the fluid phase during the preparation period.

	The noise present in each dataset is quantified by the parameter $\sigma^2$. It can be observed dataset obtained at $40~^\circ C$ / 200 bar and $30~^\circ C$ / 300 bar have similar value of $\sigma^2\approx0.07$. The slightly better results were obtained for the experiment at $50~^\circ C$ / 300 bar when $\sigma^2\approx0.05$. The noisiest dataset corresponds to $50~^\circ C$ / 200 bar when $\sigma^2\approx0.12$. All values of $\sigma^2$ are relatively low, suggesting the mathematical model can mimic the physical system.
